Moral Foundations of U.S. Political News Organizations

### 2019-01-17 pilot_manuscript.Rmd
Fixed citations
Not sure what to do for Congressional Record - it's weird

Once data collection ended, the text was scanned using the *ngram* package in *R* [@CITE_ngram]. This package includes a word count function, which was used to remove articles that came through as blank text, as well as to eliminate text picked up from the Disqus commenting system used by certain websites. At this point, duplicate articles were discarded.

@@

To analyze if news sources adhered to differences in word use based on their target audience, we utilized a multilevel model (MLM) to analyze the data. MLM is a regression technique that allows one to control for the repeated measurement and nested structured of the data, which creates correlated error [@CITE_gelman]. Using the *nlme* library in *R* [@CITE_nlme], each foundation's weighted percentage was predicated by the political lean of the news soource, using the individual news sources as a random intercept to control for the structure of the data.

@@

On September 27, the committee questioned Dr. Ford before commencing a second round of questioning for Judge Kavanaugh [@CITE_CONGRESSIONAL_RECORD]. During the intervening weeks between hearings, two more women came forward with two separate allegations of sexual assault on the part of Kavanaugh. According to Nielsen reports, more than 20 million people watched the September 27 proceedings on television [@CITE_NIELSEN]. This figure does not take into account viewers who watched online, nor does it account for viewers outside the United States. On September 28, the Senate Judiciary Committee voted to send the nomination to the Senate floor. Senator Jeff Flake of Arizona, however, lobbied for a week-long FBI investigation on Kavanaugh and the allegations facing him, which the committee, and later the President, approved. The investigation concluded with no significant findings. The Senate voted 50-48 to approve Kavanaugh's appointment on October 6, 2018 [@CITE_CONGRESSIONAL_RECORD].

@@

Using the *rvest* library in the statistical package *R*, we pulled body text for individual articles from each of the following 12 sources (identified using CSS language): *The New York Times*, *National Public Radio (NPR)*, *MSNBC*, *Slate*, *Huffington Post*, *Politico*, *Fox News*, *Breitbart*, *The Drudge Report*, *The Rush Limbaugh Show*, *The Blaze*, and *Sean Hannity*. We compiled the articles into a dataset [@CITE_rvest]. Using this dataset, we identified word count and average word count per source. This process was run for articles pertaining to Kavanaugh's nomination that were published between September 13, 2018 and October 11, 2018 inclusive. This date range was selected in reference to the widely-publicized and viewed nomination hearing on September 27, 2018. We set the start date at September 13 (two weeks before the hearing) and the end date at October 11 (two weeks after the hearing) so that we could capture a large amount of data (roughly one month) during which Kavanaugh's nomination was at its peak saturation in news coverage.

Expected material stuff
- we are going to pick liberal and conservative sources from that thing document linked stuff
- list those here:
  Sources used by LIBERALS:
  MSNBC
  Slate
  Huffington Post
  NPR
  New York Times
  Politico

  Sources used by CONSERVATIVES:
  Fox News
  Drudge Report *HEY! THIS IS MOSTLY AN AGGREGATOR!!! IS IT STILL OK?*
  Breitbart
  Rush Limbaugh Show
  The Blaze
  Sean Hannity

  DROPPED:
  Glenn Beck (does he still report "news"??)
  The Daily Show (is it wise to use satirical news for this??) - Answer = Nope
  The Guardian (not American)
  The New Yorker
  Al Jazeera America
  Buzzfeed
  PBS
  BBC
  Washington Post
  The Economist
  CNN
  NBC News
  CBS News
  Google News
  Bloomberg
  ABC News
  USA TODAY

@@

As in Experiment 1, the text was scanned using the *ngram* package in *R* at the conclusion of data collection [@CITE_ngram]. Using the package's word count function, articles that came through as blank text were removed, as well as text scraped from the Disqus commenting system. Duplicate articles were subsequently discarded.

Using the *tm* and *ngram* packages in *R*, the researchers processed the text in order to convert it to lowercase, fix spacing anomalies, and remove punctuation [@CITE_tm]. Each individual word was reduced to its stem (i.e., *diseased* was stemmed to *diseas*). Once again, the same procedure was applied to the MFD words and the words in the @Warriner2013 dataset. Using the @Warriner2013 dictionary, the words in the MFD were assigned their valence value.

>>>>

Once data collection ended, the text was scanned using the *ngram* package in *R* [@Schmidt2017]. This package includes a word count function, which was used to remove articles that came through as blank text, as well as to eliminate text picked up from the Disqus commenting system used by certain websites. At this point, duplicate articles were discarded.

@@

To analyze if news sources adhered to differences in word use based on their target audience, we utilized a multilevel model (MLM) to analyze the data. MLM is a regression technique that allows one to control for the repeated measurement and nested structured of the data, which creates correlated error [@Gelman2006]. Using the *nlme* library in *R* [@Pinheiro2017], each foundation's weighted percentage was predicated by the political lean of the news soource, using the individual news sources as a random intercept to control for the structure of the data.

@@

On September 27, the committee questioned Dr. Ford before commencing a second round of questioning for Judge Kavanaugh [@CITE_CONGRESSIONAL_RECORD]. During the intervening weeks between hearings, two more women came forward with two separate allegations of sexual assault on the part of Kavanaugh. According to Nielsen reports, more than 20 million people watched the September 27 proceedings on television [@OConnell2018]. This figure does not take into account viewers who watched online, nor does it account for viewers outside the United States. On September 28, the Senate Judiciary Committee voted to send the nomination to the Senate floor. Senator Jeff Flake of Arizona, however, lobbied for a week-long FBI investigation on Kavanaugh and the allegations facing him, which the committee, and later the President, approved. The investigation concluded with no significant findings. The Senate voted 50-48 to approve Kavanaugh's appointment on October 6, 2018 [@CITE_CONGRESSIONAL_RECORD].

@@

Using the *rvest* library in the statistical package *R*, we pulled body text for individual articles from each of the following 12 sources (identified using CSS language): *The New York Times*, *National Public Radio (NPR)*, *MSNBC*, *Slate*, *Huffington Post*, *Politico*, *Fox News*, *Breitbart*, *The Drudge Report*, *The Rush Limbaugh Show*, *The Blaze*, and *Sean Hannity*. We compiled the articles into a dataset [@Wickham2018]. Using this dataset, we identified word count and average word count per source. This process was run for articles pertaining to Kavanaugh's nomination that were published between September 13, 2018 and October 11, 2018 inclusive. This date range was selected in reference to the widely-publicized and viewed nomination hearing on September 27, 2018. We set the start date at September 13 (two weeks before the hearing) and the end date at October 11 (two weeks after the hearing) so that we could capture a large amount of data (roughly one month) during which Kavanaugh's nomination was at its peak saturation in news coverage.

Expected material stuff
- we are going to pick liberal and conservative sources from that thing document linked stuff
- list those here:
  Sources used by LIBERALS:
  Slate
  Huffington Post
  NPR
  New York Times
  Politico

  Sources used by CONSERVATIVES:
  Fox News
  Breitbart
  Rush Limbaugh Show
  The Blaze
  Sean Hannity

  DROPPED:
  Glenn Beck (does he still report "news"??)
  The Daily Show (is it wise to use satirical news for this??) - Answer = Nope
  The Guardian (not American)
  The New Yorker
  Al Jazeera America
  Buzzfeed
  PBS
  BBC
  Washington Post
  The Economist
  CNN
  NBC News
  CBS News
  Google News
  Bloomberg
  ABC News
  USA TODAY
  Drudge Report *HEY! THIS IS MOSTLY AN AGGREGATOR!!! IS IT STILL OK? The answer is NOPE*
  MSNBC *CLOSEST TO POLITICAL CENTER; buh-bye!*

@@

As in Experiment 1, the text was scanned using the *ngram* package in *R* at the conclusion of data collection [@Schmidt2017]. Using the package's word count function, articles that came through as blank text were removed, as well as text scraped from the Disqus commenting system. Duplicate articles were subsequently discarded.

Using the *tm* and *ngram* packages in *R*, the researchers processed the text in order to convert it to lowercase, fix spacing anomalies, and remove punctuation [@Feinerer2017]. Each individual word was reduced to its stem (i.e., *diseased* was stemmed to *diseas*). Once again, the same procedure was applied to the MFD words and the words in the @Warriner2013 dataset. Using the @Warriner2013 dictionary, the words in the MFD were assigned their valence value.
